LME-MPM applied to quasi-brittle fracture.

### 2020-05-19 2020_EFM_MPM_Eigensoftening.tex
Carpetas y gitignore

% \documentclass[preprint,12pt,a4paper]{elsarticle}
\documentclass[12pt,a4paper]{elsarticle}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx} % figuras
% \usepackage{subfig}
\usepackage{subfigure} % subfiguras
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

The key idea behind the eigenerosion algorithm is the computation of the
energy-release rate attendant to the failure of material point $p$,
\begin{align}
  \label{eq:energy-release-EE}
&G_p^{k+1} = \frac{C_{\epsilon}}{m_p^{k+1}}  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
&m_p^{k+1} =  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q  
\end{align}
where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
centered at $x_p^{k+1}$. The particles which lies under this sphere are
known as the $\epsilon$-neighborhood of the material point, see
\cite{Pandolfi_2012}, this concept is conveniently is sketched in
Figure \ref{fig:Failed-particles}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Particle-failed}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Failed-particles}
\end{figure}
%%%%%%%%%%%
Other parameters are, the mass of the neighborhood $m_p^{k+1}$, the
current free-energy density per unit mass  $W_q^{k+1}$ and finally a
normalizing constant $C_{\epsilon}$. 
The failure criterion consist in to consider the material point fails
when $G_p^{k+1}$ surpasses a critical energy release rate that
measures the material-specific energy, $G_F$. The convergence of this
approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proofed that it converges to the Griffith
fracture when discretization size tends to zero. It is necessary to
point out that when a material point overpass the critical energy, its
contribution to the internal forces vector is set to zero, but its
contribution to the mass matrix is preserved.\\

@@

  \includegraphics[width=0.5\textwidth]{Figures/Damage}

@@

This problem here presented is devoted to compare how much \acrshort{lme}
approximants are able to improve the result \textit{versus} standard
linear interpolation. It consists in a square plate of size $H = 1$ containing
an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
by displacement control on the outer flanks of the plate, Figure
\ref{fig:geometry-cracked-panel-mode-I}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figures/Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%
The constitutive model consider for numerical experiment is a
linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-cracked-panel-mode-I}
\end{figure}

\begin{figure}
\centering
\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
\caption{Evolution of the stress tensor magnitude for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-cracked-panel-mode-I}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/Drop_weight}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-drop-weight-impact-test}
\end{figure}

@@

% name your BibTeX data base
\bibliography{Biblio/Biblio}

>>>>

\documentclass[preprint,12pt,a4paper]{elsarticle}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx} % figuras
% \usepackage{subfig}
\usepackage{subfigure} % subfiguras
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

The key idea behind the eigenerosion algorithm is the computation of the
energy-release rate attendant to the failure of material point $p$,
\begin{align}
  \label{eq:energy-release-EE}
&G_p^{k+1} = \frac{C_{\epsilon}}{m_p^{k+1}}  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
&m_p^{k+1} =  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q  
\end{align}
where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
centered at $x_p^{k+1}$. The particles which lies under this sphere are
known as the $\epsilon$-neighborhood of the material point, see
\cite{Pandolfi_2012}, this concept is conveniently is sketched in
Figure \ref{fig:Failed-particles}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figure-Particle-failed}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Failed-particles}
\end{figure}
%%%%%%%%%%%
Other parameters are, the mass of the neighborhood $m_p^{k+1}$, the
current free-energy density per unit mass  $W_q^{k+1}$ and finally a
normalizing constant $C_{\epsilon}$. 
The failure criterion consist in to consider the material point fails
when $G_p^{k+1}$ surpasses a critical energy release rate that
measures the material-specific energy, $G_F$. The convergence of this
approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proofed that it converges to the Griffith
fracture when discretization size tends to zero. It is necessary to
point out that when a material point overpass the critical energy, its
contribution to the internal forces vector is set to zero, but its
contribution to the mass matrix is preserved.\\

@@

  \includegraphics[width=0.5\textwidth]{Figure-Damage}

@@

This problem here presented is devoted to compare how much \acrshort{lme}
approximants are able to improve the result \textit{versus} standard
linear interpolation. It consists in a square plate of size $H = 1$ containing
an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
by displacement control on the outer flanks of the plate, Figure
\ref{fig:geometry-cracked-panel-mode-I}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%
The constitutive model consider for numerical experiment is a
linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figure-Reactions-mode-I}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-cracked-panel-mode-I}
\end{figure}

\begin{figure}
\centering
\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0100-mode-I.png}}
\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0250-mode-I.png}}
\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0398-mode-I.png}}
\caption{Evolution of the stress tensor magnitude for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-cracked-panel-mode-I}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{./Figure-Drop-weight}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-drop-weight-impact-test}
\end{figure}

@@

% name your BibTeX data base
\bibliography{Biblio}

### 2020-05-19 _region_.tex
Carpetas y gitignore

\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}% \documentclass[preprint,12pt,a4paper]{elsarticle}
\documentclass[12pt,a4paper]{elsarticle}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{float}
\usepackage{subfig}
\usepackage{subfigure} % subfiguras
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

The key idea behind the eigenerosion algorithm is the computation of the
energy-release rate attendant to the failure of material point $p$,
\begin{align}
  \label{eq:energy-release-EE}
&G_p^{k+1} = \frac{C_{\epsilon}}{m_p^{k+1}}  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
&m_p^{k+1} =  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q  
\end{align}
where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
centered at $x_p^{k+1}$. The particles which lies under this sphere are
known as the $\epsilon$-neighborhood of the material point, see
\cite{Pandolfi_2012}, this concept is conveniently is sketched in
Figure \ref{fig:Failed-particles}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Particle-failed}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Failed-particles}
\end{figure}
%%%%%%%%%%%
Other parameters are, the mass of the neighborhood $m_p^{k+1}$, the
current free-energy density per unit mass  $W_q^{k+1}$ and finally a
normalizing constant $C_{\epsilon}$. 
The failure criterion consist in to consider the material point fails
when $G_p^{k+1}$ surpasses a critical energy release rate that
measures the material-specific energy, $G_F$. The convergence of this
approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proofed that it converges to the Griffith
fracture when discretization size tends to zero. It is necessary to
point out that when a material point overpass the critical energy, its
contribution to the internal forces vector is set to zero, but its
contribution to the mass matrix is preserved.\\

@@

  \includegraphics[width=0.5\textwidth]{Figures/Damage}

@@

This problem here presented is devoted to compare how much \acrshort{lme}
approximants are able to improve the result \textit{versus} standard
linear interpolation. It consists in a square plate of size $H = 1$ containing
an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
by displacement control on the outer flanks of the plate, Figure
\ref{fig:geometry-cracked-panel-mode-I}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figures/Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%
The constitutive model consider for numerical experiment is a
linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-cracked-panel-mode-I}
\end{figure}

\begin{figure}
\centering
\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
\caption{Legos.}
\label{fig:Stress-cracked-panel-mode-I}
\end{figure}

Edge_cracked_square_panel_in_mode_I_Stress_0250.png
Edge_cracked_square_panel_in_mode_I_Stress_0398.png

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/Drop_weight}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-drop-weight-impact-test}
\end{figure}

@@

% name your BibTeX data base
\bibliography{Biblio/Biblio}

\end{document}
\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-867) }

>>>>

\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}\documentclass[preprint,12pt,a4paper]{elsarticle}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{float}
\usepackage{graphicx} % figuras
% \usepackage{subfig}
\usepackage{subfigure} % subfiguras
\usepackage{color}
\usepackage{soul}
\usepackage{cancel}

@@

The key idea behind the eigenerosion algorithm is the computation of the
energy-release rate attendant to the failure of material point $p$,
\begin{align}
  \label{eq:energy-release-EE}
&G_p^{k+1} = \frac{C_{\epsilon}}{m_p^{k+1}}  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
&m_p^{k+1} =  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q  
\end{align}
where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
centered at $x_p^{k+1}$. The particles which lies under this sphere are
known as the $\epsilon$-neighborhood of the material point, see
\cite{Pandolfi_2012}, this concept is conveniently is sketched in
Figure \ref{fig:Failed-particles}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Particle-failed}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Failed-particles}
\end{figure}
%%%%%%%%%%%
Other parameters are, the mass of the neighborhood $m_p^{k+1}$, the
current free-energy density per unit mass  $W_q^{k+1}$ and finally a
normalizing constant $C_{\epsilon}$. 
The failure criterion consist in to consider the material point fails
when $G_p^{k+1}$ surpasses a critical energy release rate that
measures the material-specific energy, $G_F$. The convergence of this
approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proofed that it converges to the Griffith
fracture when discretization size tends to zero. It is necessary to
point out that when a material point overpass the critical energy, its
contribution to the internal forces vector is set to zero, but its
contribution to the mass matrix is preserved.\\

@@

  \includegraphics[width=0.5\textwidth]{Damage}

@@

This problem here presented is devoted to compare how much \acrshort{lme}
approximants are able to improve the result \textit{versus} standard
linear interpolation. It consists in a square plate of size $H = 1$ containing
an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
by displacement control on the outer flanks of the plate, Figure
\ref{fig:geometry-cracked-panel-mode-I}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%
The constitutive model consider for numerical experiment is a
linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Reactions_displacements_square_panel_mode_I}
  \caption{Evolution of the reaction forces plotted \textit{versus}
    the imposed displacement for linear interpolation technique and
    the \acrshort{lme} approximants.}
  \label{fig:Reactions-cracked-panel-mode-I}
\end{figure}

\begin{figure}
\centering
\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
\caption{Evolution of the stress tensor magnitude for linear
  interpolation (pictures in the left side), and \acrshort{lme}
  (pictures in the right side). Both simulations performed with an
  eigenerosion algorithm.}
\label{fig:Stress-cracked-panel-mode-I}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{./Drop_weight}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-drop-weight-impact-test}
\end{figure}

@@

% name your BibTeX data base
\bibliography{Biblio}

\end{document}
\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-868) }
